---
#title: "Untitled"
#author: "DABIRE Ives Ulrich"
#date: "`r Sys.Date()`"
output:
  pdf_document:
    number_sections: true
    toc: true
    toc_depth: 2
    latex_engine: xelatex
    keep_tex: true
    includes:
      in_header: header.tex
      before_body: titlepage.tex
#mainfont: "Times New Roman"
fontsize: 12pt
linestretch: 1.5
geometry: margin=1in
---

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#tinytex::install_tinytex()
```

## R Markdown

This is an R Markdown[^1] document. When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this: For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

```{r cars}
summary(cars)
```

[^1]: *Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents.* 

\newpage

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
